---
title: "Business Intelligence Project"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        | 136788 |
| **Student Name**                             | Derrick Nyaga |
| **BBIT 4.2 Group**                           | C |
| **BI Project Group Name/ID (if applicable)** | ... |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset

library(readr)
politifact_factcheck_data <- read_csv(
  "data/politifact_factcheck_data.csv"
)

### Source:

The dataset that was used can be downloaded here: *https://www.kaggle.com/datasets/rmisra/politifact-fact-check-dataset*

### Reference:

*\<Cite the dataset here using APA\>\
Misra, R. (2022, September).Politifact Fact Check Dataset.[Data set].ResearchGate. https://doi.org/10.13140/RG.2.2.29923.22566


```{r Dataset Loader}
library(readr)
politifact_factcheck_data <- read_csv(
  "data/politifact_factcheck_data.csv"
)

# Provide the executable R code inside the various code chunks as guided by the lab work.
```

...to be continued
